### 2017-11-20 Risk analysis/Text/Layout/Layout/MSc_layout_Fabian.tex
Restructuring cjhapters
Layout changes
Some text progress (methods)
Uncertainty parameters seem good!
To Do: Implement return of trap control mechanism:
Leak - Spill - Juxta... maybe SFF/Throw Likelihood?
More models running. Updated text and figures
Working on 3D results text
Figures in Appendix. Next: Discussion!
Continued discussion text (1 page)
Text progress

\documentclass[a4paper,11pt]{MScThesis}
%
%\usepackage{pifont}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subcaption}
\graphicspath{Figures/}
%\usepackage{mathpazo}
\mscName{Fabian Antonio Stamm}
\mscDate{\today}
\mscTitle{Test}
\mscSubTitle{Subtitle}
\mscKeyWords{thesis, msc, subject}
%
%\mscBackPicture{2660PF3}    % eps of 21 * 29.7 cm
\mscReaderOne{Prof. Florian Wellmann, Ph.D.}
\mscReaderTwo{Prof. Dr. Janos Urai}
\mscReaderThree{Miguel de la Varga, M.Sc.}
%\mscReaderFour{}
%
\setThesisInfo
%
\begin{document}
%
%============================= Front matter ========================================
\frontmatter %
%
% Make a hell of a lot of title pages
    \maketitle
%
% Abstract
	\nonumchap{Abstract}

Please pay particular attention to the preparation of your abstract; use this text as a guide. Every master thesis report must be accompanied by an informative abstract of no more than one paragraph (max 300 words). The abstract should be self-contained. No references, figures, tables, or equations are allowed in an abstract. Do not use new terminology in an abstract unless it is defined or is well-known from the literature. The abstract must not simply list the topics covered in the paper but should (1) state the scope and principal objectives of the research, (2) describe the methods used, (3) summarize the results, and (4) state the principal conclusions. Do not refer to the master thesis report itself in the abstract. For example, do not say, "In this thesis we will discuss". Furthermore the abstract must stand alone as a very short version of the master thesis report rather than as a description of the contents. Remember that the abstract will be the first and most widely read portion of the master thesis report. Readers will be influenced by the abstract to the point that they decide to read the master thesis report or not.

@@

%
% table of contents, (\toc or \toclof or \tocloflot )
    \tocloflot
%
% Nomenclature
    \printnomencl %
%
% Acronyms
    \nonumchap{Acronyms} %
    %
    \begin{acronym}%
        \acro{RWTH}{Aachen University}%
    \end{acronym}%
    %
    \cleardoublepage%
%
%
%============================= Main matter =========================================
%
\mainmatter
%
% Introduction
\include{chapter1} % notice how the reference to the introduction takes place.. It refers to the name.tex

\cleardoublepage

		\include{chapter2_methods}
		\include{chapter3_1Dcase}
		\include{chapter4_3Dcase}

@@

>>>>

\documentclass[a4paper,11pt]{MScThesis}
%
%\usepackage{pifont}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{booktabs}
\graphicspath{Figures/}
%\usepackage{mathpazo}
\mscName{Fabian Antonio Stamm}
\mscDate{\today}
\mscTitle{Bayesian Decision Theory in Structural Geological Modeling}
\mscSubTitle{How Reducing Uncertainties Affects Reservoir Value Estimations}
\mscKeyWords{thesis, msc, subject}
%
%\mscBackPicture{2660PF3}    % eps of 21 * 29.7 cm
\mscReaderOne{Prof. Florian Wellmann, Ph.D.}
\mscReaderTwo{Prof. Dr. Janos Urai}
\mscReaderThree{Miguel de la Varga, M.Sc.}
%\mscReaderFour{}
%
\setThesisInfo
%
\begin{document}
%
%============================= Front matter ========================================
\frontmatter %
%
% Make a hell of a lot of title pages
    \maketitle
%
% Abstract
	\nonumchap{Abstract}
Bayesian methods are an intuitive approach to inference and subsequent decision-making, relatable to a wide spectrum of problems. Hydrocarbon exploration and production is a high-risk, high-reward sector in which good decision-making is indispensable. However, actors in this field are faced by numerous uncertainties that have to be considered. Structural geological modeling is of central importance for the estimation of uncertain hydrocarbon accumulations in potential reservoirs. Recent developments have shown, that such modeling can be regarded as a Bayesian inference problem. This allows for the incorporation of additional geological information as likelihood functions in a probabilistic framework and a consequent reduction of model uncertainties.

---
Please pay particular attention to the preparation of your abstract; use this text as a guide. Every master thesis report must be accompanied by an informative abstract of no more than one paragraph (max 300 words). The abstract should be self-contained. No references, figures, tables, or equations are allowed in an abstract. Do not use new terminology in an abstract unless it is defined or is well-known from the literature. The abstract must not simply list the topics covered in the paper but should (1) state the scope and principal objectives of the research, (2) describe the methods used, (3) summarize the results, and (4) state the principal conclusions. Do not refer to the master thesis report itself in the abstract. For example, do not say, "In this thesis we will discuss". Furthermore the abstract must stand alone as a very short version of the master thesis report rather than as a description of the contents. Remember that the abstract will be the first and most widely read portion of the master thesis report. Readers will be influenced by the abstract to the point that they decide to read the master thesis report or not.

@@

%
% table of contents, (\toc or \toclof or \tocloflot )
    \tocloflot
%
% Nomenclature
    \printnomencl %
%
% Acronyms
    \nonumchap{Acronyms} %
    %
    \begin{acronym}%
        \acro{RWTH}{Aachen University}%
    \end{acronym}%
    %
    \cleardoublepage%
%
%
%============================= Main matter =========================================
%
\mainmatter
%
% Introduction
%\include{chapter1} % notice how the reference to the introduction takes place.. It refers to the name.tex

\cleardoublepage
		\include{chapter1}
		\include{chapter2_methods}
		\include{chapter3_results}
		\include{chapter4_discussion}
		%\include{chapter5_conclusion}
		%\include{chapter3_1Dcase}
		%\include{chapter4_3Dcase}

@@

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.62\textwidth]{Figures/Appendix/CSV_input1}
    	\caption{....}\label{fig:CSV_input1}
    \end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.62\textwidth]{Figures/Appendix/CSV_input2}
		\caption{....}\label{fig:CSV_input2}
	\end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=1\textwidth]{Figures/Appendix/CSV_input3}
		\caption{....}\label{fig:CSV_input3}
	\end{figure}

    \begin{figure}[p!]
    	\centering
    	\includegraphics[width=1\textwidth]{Figures/Appendix/ML4}
    	\caption{....}\label{fig:ML4}
    \end{figure}

### 2017-11-20 Risk analysis/Text/Layout/Layout/chapter3_results.tex
Text progress

		\section{3D geological model results}
		In the following, results from applying the methods on the artificial 3D structural model are presented. Several representative examples of posterior models based on the use of different likelihoods are referenced to the original prior model. The following measures are central to the comparison of simulation results: (1) information entropy, (2) occurrence of trap control mechanisms, (3) resulting recoverable oil volumes and (3) consequent realization of expected losses and related Bayes actions (i.e. decisions).

@@

		Consequently, applying the custom loss function on this distribution results in divergent Bayes actions for the different risk-affine actors (see Figure \ref{fig:M_prior} (b)). Although all actors find their estimates to be positive, only the risk-neutral to risk-friendliest actors come close to the described positive mode of the distribution ($ROV > 3*10^6$ m$^3$). Risk-averse individuals bid on significantly lower estimates. It can also be observed that expected losses seem to be generally lower for risk-affine actors. The divergence of different Bayes actions presumably resulted from the bimodality of the $ROV$ probability distribution.

		\subsection{Posterior model I: Seal and reservoir likely thick}
		\begin{table}[h]
			\centering
			\begin{tabular}{lrr} 
				\toprule
				Model I - Likelihoods: layer thicknesses (normal distributions)\\  
				\midrule 
				Formation & $\mu$ [m] & $\sigma$ [m]\\ 
				\midrule 
				Sandstone 2 & 150 & 30 \\
				Shale (Seal) & 350 & 30\\ 
				Sandstone 1 (Reservoir) & 250 & 30 \\
				\bottomrule
			\end{tabular}
			\caption{Layer thickness likelihoods determined by normal distributions as used for posterior model I.}
			\label{tab:ML1_likelihoods}
		\end{table}
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML1}
			\caption{....}\label{fig:ML1}
		\end{figure}		
		For the simulation of this first posterior model, thickness likelihoods for the three central layers were included into the probabilistic model. These were defined in a way that reinforced the probabilities of the relevant layers to be significantly thick (see Table \ref{tab:ML1_likelihoods}). Respective results are summarized in Figure \ref{fig:ML1}.\\
		Considering the changes in information entropy, it can be seen that the uncertainty about layer interface positions in $z$ was clearly reduced in the footwall. Information entropy was also decreased in the middle section of the hanging wall, but remained high in upper and lower parts, presumably due to the remaining influence of the offset uncertainty.\\
		Regarding trap volume control (Figure \ref{fig:ML1} (c)), only spill point-related migration ("SPILL POINT") and cross-fault leakage due to juxtaposition with permeable layers below the seal in the hanging wall ("LEAK UNDER") remain relevant in the posterior model. As no occurrences of leakage through overlying layers was observed, the two other mechanisms increased in frequency, while staying proportionally the same to one another. It can be presumed, that by introducing the respective likelihoods, a high thickness of the seal was ensured, as can also be recognized in Figure \ref{fig:ML1} (b). This not only made stratigraphic leakage in this model impossible, but also enforced a favorable $SSF$. A minor emergence of unrecognized control factors ("UNCLEAR") suggests that, for a few iterations, the model was possibly not correctly computable or the structural analysis failed for a different reason.\\
		The bulk that accounted for the positive mode in the prior $ROV$ distribution was raised and shifted laterally to higher values, while the probability of failure ($ROV = 0$) was diminished significantly (see Figure Figure \ref{fig:ML1} (d)). This can presumably be explained by the disappearing of leakage to overlying formations as a trap control mechanism, which was programmed to always lead to complete failure of the trap volume.\\
		As the probability of failure and thus the bimodality of the probability distribution disappeared, all Bayes actions were shifted to higher estimates, most significantly those of the two risk-averse individuals (see Figure \ref{fig:ML1} (e). These have thus converged into an area of similar expectations. Additionally, expected losses were lowered overall. The posterior state of knowledge, provided by the updated model, encouraged even the most risk-averse decision-maker to expect recoverable oil volumes from 3.5 million m$^3$ upwards.

		\subsection{Posterior model II: Likely thin reservoir formation}%ML3
		For the second model, thickness likelihoods were defined in a way that reinforced the probability of a very thick seal but at the same time restricted the reservoir formation to a likely significantly thinner thickness of around 50 m (see Table in Appendix). The results (see Appendix) are very similar, in fact practically identical, to those of model I above. This can be explained by the influence of leak and spill point. As the shape of the general structure itself was not defined to be uncertain, the position of the anticlinal spill point relative to the fault top remains mostly unchanged, irrespective of layer thickness variations. Thus, reservoir thickness is only a secondary factor to trap volume control. Assuming fixed values for all other parameters, the maximum fill horizon is most likely the same for a 300 m as for a 50 m thick reservoir unit. The thickness of the reservoir only becomes significant, if it is thin enough to locate the respective layer bottom above the leak and spill point depth in the trap section. Ultimately, the spill point appears to be the primariy limiting factor to maximum trap fill. It can furthermore be derived from this that the maximum trap volume potential, as defined by the given structural features, is already represented in the $ROV$ probability distribution of the prior model. Examining this in Figure \ref{fig:ML1} (d), it seems that this overall maximum volume is found at approximately 5.7 millon m$3$. Higher values were not observed in any other model realization and are presumed to be unattainable due to the restriction given by the spill point.

		\subsection{Posterior model III: Likely very thin seal}%ML2
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML2}
			\caption{....}\label{fig:ML2}
		\end{figure}
		Results from this third model show that in contrast to the reservoir thickness, seal thickness is a primary and decisive factor for the manifestation of a reliable trap structure. Using likelihoods which favor a thick reservoir, but only a thin seal of about 50 m thickness, leakage due to juxtaposition with seal-overlying formations across the fault ("LEAK OVER") becomes the primary mechanism for trap volume control (see Figure \ref{fig:ML2} (c). It can be recognized in Figure \ref{fig:ML2} (b) that, while uncertainty was reduced clearly in the footwall, it remains high in the hanging wall. The state of information entropy furthermore suggests that the seal layer frequently appeared significantly deeper in the hanging wall than in the footwall. Combined with a generally very thin seal, this allowed for the occurrence of high displacement to seal thickness ratios, i.e. a high $SSF$. Thus, frequent surpassing of the critical $SSF$ and subsequent fault seal breaching were enabled. It is additionally apparent in Figure \ref{fig:ML2} (b), that while fault-related leakage has become predominant, control by the spill point was suppressed to be widely irrelevant in this posterior model.\\	%It is suggested by the footwall information entropy in Figure \ref{label} (b), that the general shape of the structure has been flattened.
		A dramatically higher probability of complete trap failure is induced by the high frequency of cross-fault leakage to overlying formations. Consequently, the bulk of the posterior $ROV$ probability distribution is shifted to a volume of zero, as depicted in Figure \ref{fig:ML2} (d). Any positive trap volumes have become highly improbable.\\
		Bayes actions changed accordingly. Given this posterior $ROV$ distribution, all actors find their minimum of expected loss at $ROV = 0$, which equals the decision to "take no action" (see Figure \ref{fig:ML2} (e)). It has to be pointed out that all Bayes actions are found at the same point due to the lack of negative values into which more risk-averse actors would presumably move, given the possibility. This is a difference to the score system implemented for the 1D geological model evaluation. Volumes cannot be negative, thus, Bayes actions cannot be shifted past the limit of $ROV = 0$. Compared to the prior model, expected losses were decreased overall, but are higher for more risk-friendly individuals at the minimum.

		\subsection{Posterior model IV: SSF likelihood reinforcing trap reliability}%ML4
		For this fourth model, thickness likelihoods were chosen to be comparable to those of model I, i.e. supporting the probability of thick layers in general. Additionally, a $SSF$-related likelihood function was implemented. With a mean of 1.5 and a standard deviation of 0.5, it was chosen to mostly reinforce the likelihood of a $SSF$ below the critical value of $SSF_c = 3$.\\
		In Figure \ref{ML4} (b), it can be seen that the uncertainty about the position of interfaces in the footwall was greatly reduced for all layers. In the hanging wall, information entropies remained high but were shifted upwards and mainly concentrated in an area that is juxtaposed to the footwall seal formation.\\
		In the resulting $ROV$ distribution, the possibility of trap failure was completely extinguished, while the probability of high volumes in the range between 3.5  and 5 million m$^3$ was significantly increased. Mean and median are found at almost the same value, but the bulk of the distribution found in this range appears to be slightly bimodal in itself, resembling approximately the shape of two normal distributions overlapping around a value of 4 million m$m^3$.\\
		Accordingly, Bayes actions converged within this range of positive values. Considering the two modes in this range, risk-averse to risk-neutral bids remained in the middle of the mode of lower volumes, while risk-friendly actors were encouraged to estimate higher volumes as found in the second mode. Overall, significant convergence was achieved, also in respect to expected losses.\\		
		The importance of a reliable seal is once again emphasized by these results. Reliable fault sealing was favored by the chosen $SSF$ likelihood. It should be pointed out that computation of the complete model is required to attain the $SSF$. This value is furthermore characterized by a complex interdependence with other parameters and is most directly related to layer thicknesses and fault offset. For this reason, information entropy and offset uncertainty in the hanging wall was not greatly reduced. However, the certainty about the ratio of displacement to layer thicknesses was improved by using the $SSF$ in a likelihood function.

		\subsection{Posterior model V: Controversial information about the Shale Smear Factor}%ML5
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML5}
			\caption{....}\label{fig:ML5}
		\end{figure}
		In this last case example, no thickness likelihoods, only a $SSF$-related likelihood was used. In contrast to model IV, this was chosen to narrow the probability of the $SSF$ to be around the threshold of its critical value, by basing it on a normal distribution with a mean of 3 and a standard deviation of 0.3.\\
		Results are relatively similar to those of the prior model. It is notable that the information entropy regarding the position of layer boundaries in the footwall was decreased, while the entropy seems to have been raised significantly in the hanging wall (Figure \ref{fig:ML5} (b)). Furthermore, an increase in the relevance of cross-fault leakage to overlying formations ("LEAK OVER") as a trap volume mechanism (increase from $\sim13\%$ to $\sim18\%$) was observed (Figure \ref{fig:ML5} (c)). Consequently, the bimodality between the bulk of positive values and the probability of complete failure in the $ROV$ distribution was apparently reinforced. This is also indicated by a shift of mean and median to lower volumes (Figure \ref{fig:ML5} (d)). Accordingly, a higher degree of decision divergence, i.e. a greater separation of different Bayes actions, was induced (Figure \ref{fig:ML5} (e)). Expected losses of the minima were raised as well.\\
		It is notable that the implementation of a likelihood which can be expected to significantly decrease the $SSF$ related uncertainty, overall leads to an amplification of the duality in the $ROV$ probability distribution and to dispersion of different risk-affine decisions. This effect is presumably caused by conservation of decisive uncertainty between "success" and complete failure of the trap, by narrowing the probability of the $SSF$ to be around its critical value.

>>>>

		\section{3D geological model results}
		In the following, results from applying the methods on the artificial 3D structural model are presented. Several representative examples of posterior models based on the use of different likelihoods are referenced to the original prior model. For all model simulations, 1000 sampling steps were conducted, with a burn-in phase of 50 iterations for MCMC sampling. The following measures are central to the comparison of results: (1) information entropy, (2) occurrence of trap control mechanisms, (3) resulting recoverable oil volumes and (3) consequent realization of expected losses and related Bayes actions (i.e. decisions).

@@

		Consequently, applying the custom loss function on this distribution resulted in divergent Bayes actions for the different risk-affine actors (see Figure \ref{fig:M_prior} (b)). Although all actors found their estimates to be positive, only the risk-neutral to risk-friendliest actors came close to the described positive mode of the distribution ($ROV > 3*10^6$ m$^3$). Risk-averse individuals bid on significantly lower estimates. It can also be observed that expected losses resulted to be generally lower for risk-affine actors. It can be presumed that the divergence of different Bayes actions was caused the bimodality of the $ROV$ probability distribution.

		\subsection{Posterior model I: Seal and reservoir likely thick}
		\begin{table}[h]
			\centering
			\begin{tabular}{lrr} 
				\toprule
				Model I - Likelihoods: layer thicknesses (normal distributions)\\  
				\midrule 
				Formation & $\mu$ [m] & $\sigma$ [m]\\ 
				\midrule 
				Sandstone 2 & 150 & 30 \\
				Shale (Seal) & 350 & 30\\ 
				Sandstone 1 (Reservoir) & 250 & 30 \\
				\bottomrule
			\end{tabular}
			\caption{Layer thickness likelihoods determined by normal distributions as used for posterior model I.}
			\label{tab:ML1_likelihoods}
		\end{table}
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML1}
			\caption{....}\label{fig:ML1}
		\end{figure}		
		For the simulation of this first posterior model, thickness likelihoods for the three central layers were included in the probabilistic model. These were defined in a way that reinforced the probabilities of the relevant layers to be significantly thick (see Table \ref{tab:ML1_likelihoods}). Respective results are summarized in Figure \ref{fig:ML1}.\\
		Considering the changes in information entropy, it can be seen that the uncertainty about layer interface positions in $z$ was clearly reduced in the footwall. Information entropy was also decreased in the middle section of the hanging wall, but remained high in upper and lower parts, presumably due to the remaining influence of the offset uncertainty.\\
		Regarding trap volume control (Figure \ref{fig:ML1} (c)), only spill point-related migration ("SPILL POINT") and cross-fault leakage due to juxtaposition with permeable layers below the seal in the hanging wall ("LEAK UNDER") remained relevant in the posterior model. As no occurrences of leakage through overlying layers were observed, the two other mechanisms increased in frequency, while staying proportionally the same to one another. It can be presumed, that by introducing the respective likelihoods, a high thickness of the seal was ensured, as can also be recognized in Figure \ref{fig:ML1} (b). This not only made stratigraphic leakage in this model impossible, but also enforced a favorable $SSF$. A minor emergence of unrecognized control factors ("UNCLEAR") suggests that, for a few iterations, the model was possibly not correctly computable or the structural analysis failed for a different reason.\\
		The bulk that accounted for the positive mode in the prior $ROV$ distribution was raised and shifted laterally to higher values, while the probability of failure ($ROV = 0$) was diminished significantly (see Figure Figure \ref{fig:ML1} (d)). This can presumably be explained by the disappearing of leakage to overlying formations as a trap control mechanism, which was programmed to always lead to complete failure of the trap volume.\\
		As the probability of failure and thus the bimodality of the probability distribution disappeared, all Bayes actions were shifted to higher estimates, most significantly those of the two risk-averse individuals (see Figure \ref{fig:ML1} (e). These have thus converged into an area of similar expectations. Additionally, expected losses were lowered overall. The posterior state of knowledge, provided by the updated model, encouraged even the most risk-averse decision-maker to expect recoverable oil volumes from 3.5 million m$^3$ upwards.

		\subsection{Posterior model II: Likely thin reservoir formation}%ML3
		For the second model, thickness likelihoods were defined in a way that reinforced the probability of a very thick seal but at the same time restricted the reservoir formation to a likely significantly thinner thickness of around 50 m (see Table in Appendix). The results (see Figure \ref{fig:ML3}) are very similar, in fact almost identical, to those of model I above. This can be explained by the influence of leak and spill point. As the shape of the general structure itself was not defined to be uncertain, the position of the anticlinal spill point relative to the fault top remains mostly unchanged, irrespective of layer thickness variations. Thus, reservoir thickness is only a secondary factor to trap volume control. Assuming fixed values for all other parameters, the maximum fill horizon is most likely the same for a 300 m as for a 50 m thick reservoir unit. The thickness of the reservoir only becomes significant, if it is thin enough to locate the respective layer bottom above the leak and spill point depth in the trap section. Ultimately, the spill point appears to be the primariy limiting factor to maximum trap fill. It can furthermore be derived from this that the maximum trap volume potential, as defined by the given structural features, is already represented in the $ROV$ probability distribution of the prior model. After examining Figure \ref{fig:ML1} (d), it seems that this overall maximum volume is found at approximately 5.7 millon m$3$. Higher values were not observed in any other model realization and are presumed to be unattainable due to the restriction given by the spill point.

		\subsection{Posterior model III: Likely very thin seal}%ML2
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML2}
			\caption{....}\label{fig:ML2}
		\end{figure}
		Using likelihoods which favor a thick reservoir, but only a thin seal of about 50 m thickness, leakage due to juxtaposition with seal-overlying formations across the fault ("LEAK OVER") became the primary mechanism for trap volume control (see Figure \ref{fig:ML2} (c). It can be recognized in Figure \ref{fig:ML2} (b) that, while uncertainty was reduced clearly in the footwall, it remains high in the hanging wall. The state of information entropy furthermore suggests that the seal layer frequently appeared significantly deeper in the hanging wall than in the footwall. Combined with a generally very thin seal, this allowed for the occurrence of high displacement to seal thickness ratios, i.e. a high $SSF$. Thus, frequent surpassing of the critical $SSF$ and subsequent fault seal breaching were enabled. It is additionally apparent in Figure \ref{fig:ML2} (b), that while fault-related leakage became predominant, control by the spill point was suppressed to be widely irrelevant in this posterior model.\\	%It is suggested by the footwall information entropy in Figure \ref{label} (b), that the general shape of the structure has been flattened.
		A dramatically higher probability of complete trap failure was induced by the high frequency of cross-fault leakage to overlying formations. Consequently, the bulk of the posterior $ROV$ probability distribution was shifted to a volume of zero, as depicted in Figure \ref{fig:ML2} (d). Any positive trap volumes have become highly improbable.\\
		Bayes actions changed accordingly. Given this posterior $ROV$ distribution, all actors found their minimum of expected loss at $ROV = 0$, which equals the decision to "take no action" (see Figure \ref{fig:ML2} (e)). It has to be pointed out that all Bayes actions were found at the same point due to the lack of negative values into which more risk-averse actors would presumably have moved, given the possibility. This poses a difference to the score system implemented for the 1D geological model evaluation. As volumes cannot be negative, Bayes actions cannot be shifted past the limit of $ROV = 0$. Compared to the prior model, expected losses were decreased overall, but are higher for risk-friendlier individuals at the minimum. Results from this third model show that in contrast to the reservoir thickness, seal thickness is a primary and decisive factor for the manifestation of a reliable trap structure.

		\subsection{Posterior model IV: SSF likelihood reinforcing trap reliability}%ML4
		For this fourth model, thickness likelihoods were chosen to be comparable to those of model I, i.e. supporting the probability of thick layers in general. Additionally, a $SSF$-related likelihood function was implemented. With a mean of 1.5 and a standard deviation of 0.5, it was chosen to mostly reinforce the likelihood of a $SSF$ below the critical value of $SSF_c = 3$.\\
		In Figure \ref{ML4} (b), it can be seen that the uncertainty about the position of interfaces in the footwall was greatly reduced for all layers. In the hanging wall, information entropy remained high but was shifted upwards and mainly concentrated in an area that is juxtaposed to the footwall seal formation.\\
		In the resulting $ROV$ distribution, the possibility of trap failure was completely extinguished, while the probability of high volumes in the range between 3.5  and 5 million m$^3$ was significantly increased. Mean and median are found at almost the same value, but the bulk of the distribution found in this range appears to be slightly bimodal in itself, resembling approximately the shape of two normal distributions overlapping around the value of 4 million m$^3$.\\
		Accordingly, Bayes actions converged within this range of positive values. Considering the two modes in this range, risk-averse to risk-neutral bids remained in the middle of the mode of lower volumes, while risk-friendly actors were encouraged to estimate higher volumes as found in the second mode. Overall, significant convergence was achieved, also in respect to expected losses.\\		
		The importance of a reliable seal is once again emphasized by these results. Reliable fault sealing was favored by the chosen $SSF$ likelihood. It should be pointed out that computation of the complete model is required to attain the $SSF$. This value is furthermore characterized by a complex interdependence with other parameters and is most directly related to layer thicknesses and fault offset. For this reason, information entropy and offset uncertainty in the hanging wall were not greatly reduced. However, the certainty about the ratio of displacement to layer thicknesses was presumably improved by using the $SSF$ in a likelihood function.

		\subsection{Posterior model V: Controversial information about the Shale Smear Factor}%ML5
		\begin{figure}[p!]
			\centering
			\includegraphics[width=1\textwidth]{Figures/ML5}
			\caption{....}\label{fig:ML5}
		\end{figure}
		In this last case example, no thickness likelihoods, only a $SSF$-related likelihood was used. In contrast to model IV, this was chosen to narrow the probability of the $SSF$ to be around the threshold of its critical value, by basing it on a normal distribution with a mean of 3 and a standard deviation of 0.3.\\
		Results are relatively similar to those of the prior model. It is notable that the information entropy regarding the position of layer boundaries in the footwall was decreased, while the entropy seems to have been raised significantly in the hanging wall (Figure \ref{fig:ML5} (b)). Furthermore, an increase in the relevance of cross-fault leakage to overlying formations ("LEAK OVER") as a trap volume mechanism (increase from $\sim13\%$ to $\sim18\%$) was observed (Figure \ref{fig:ML5} (c)). Consequently, the bimodal character between the bulk of positive values and the probability of complete failure in the $ROV$ distribution was reinforced. This is also indicated by a shift of mean and median to lower volumes (Figure \ref{fig:ML5} (d)). Accordingly, a higher degree of decision divergence, i.e. a greater separation of different Bayes actions, was induced (Figure \ref{fig:ML5} (e)). Expected losses of these minima were raised as well.\\
		It is notable that the implementation of a likelihood function, which can be expected to significantly decrease the $SSF$ related uncertainty, overall leads to an amplification of the duality in the $ROV$ probability distribution and to dispersion of differently risk-affine decisions. This effect is presumably caused by conservation of decisive uncertainty between "success" and complete failure of the trap, due to narrowing of the $SSF$ probability around its critical value.
